Source Summaries

### 2020-02-23 paper/sourceSummaries/summary4.tex
initial commit
added summary four

@@

@@

@@

@@

@@

>>>>

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{OSDPseiwgDOD}

@@

\noindent
The authors review the Open Supervised Device Protocol, how it wworks, what it supports, the messages sent, and the legal implications of using the protocol in DoD facilities.  They go in depth on the specific functioning of the protocol, the messages it sends, and the wiring necessary for it.  The authors also compare it to the Wiegand protocol, covering the differences between them and the possible issues with upgrading from Wiegand to OSDP.

@@

\noindent
The authors implement Systems theory in this article.  They observe how OSDP interfaces with other systems and how it has been implemented without attempting to attack it in any way.

@@

\noindent
They authors surveyed multiple suppliers of OSDP compatible devices and they reviewed numerous papers on OSDP.  There was no hands on research done.

@@

\noindent
They find that OSDP is "not yet widely adopted" and it is not explicitly called for in various legal compliances.  They also found that vendors have managed to keep Wiegand relevant but it is not able to support high levels of assurance.  The authors claim that vendors use "FICAM as a selling point more than OSDP" but if OSDP is associated with FICAM it will be implemented more often.

@@

\noindent
The authors indirectly recommend to "more clrealy associate" OSDP with FICAM guidance to increase the usage of it.
